Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-23 presentation-plan/presentation-plan.tex
First start for the summary of Incremental Aggregation Plan

%%%%%%%%%%%%%%%%%%%%%%% file ff-replan.tex %%%%%%%%%%%%%%%%%%%%%%%%
%
% 	Presentation Plan Arian Stolwijk & Imara Speek
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

>>>>

@@

\subsection{FF-Replan: A Baseline for Probabilistic Planning}

@@

\subsection{Incremental Plan Aggregation for Generating Policies in MDPs}

Markov Decision Processes (MDPs) is the best known formalism for planning under
uncertainty. It can however be computationally intensive if large parts of the
policies are tried to optimize at once. Most recent MDP planning techniques are
using the following steps as a basis approach:

\begin{enumerate}
	\item Take MDP problem
	\item ``Determize''  it into a classical planning problem
	\item Generate sequence of actions that represent a possible exectution
			path
	\item MDP planner executes plan:
		\begin{itemize}
			\item If goal is reached, reports success
			\item Otherwise algorithm generates a new plan from failed state of the world
		\end{itemize}
\end{enumerate}
